Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations

### 2018-01-16 Thesis/structure.tex
Exclude URLs from bibliography

\usepackage[backend=bibtex,style=nejm,sorting=none,autocite=superscript,articledoi=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
%\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[nottoc]{tocbibind}

>>>>

\usepackage[backend=bibtex,style=nejm,sorting=none,autocite=superscript,articledoi=true,url=false]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
%\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[nottoc]{tocbibind}
